Progress Report

### 2020-08-28 documentation/Optimization Work/08_27_20.tex
Resolved bug causing conflict with theory and numerical (need perfect CSI at Tx)

In the following, we will assume that a matched filter is used at transmitter. Further we will evaluate the performance of the system using the Expected Mean Square Error given by 

@@

Note that we are using the full information of the current channel in order to estimate the optimal phases at the IRS. 
In order to minimize the overhead of pilot acquisition, we estimate the CSE in the following manner. In the following we assume that the elements of the IRS can not only adjust the phases of the impinging waves but may also be "turned off" such that they are not included in the channel.

@@

	In order to first transmit matched filter we leave all IRS elements \emph{on}. Assuming that we perfectly estimate the entire channel $\mH_{Total}$, we will not have sufficient information to estimate the individual components of the channel $\mathbf{h}_{2,i}\mathbf{h}^T_{1,i}$ and thus we cannot optimize with respect to $\phi_i $.

@@

	By turning on a specific IRS element (can we use patterns using the correlation?) and sending additional pilots, we can estimate 

@@

E\left[\|  \vs - (\mG +  \mH_1 + \Sigma_{i=1}^{1} \phi_i \mathbf{h}_{2,i}\mathbf{h}^T_{1,i})(\mG +  \mH_1 + \Sigma_{i=1}^{1} \phi_i \mathbf{h}_{2,i}\mathbf{h}^T_{1,i}) \|^2 \right]

@@

@@

	cross types (e.g $(\phi_i \mathbf{h}_{2,i}\mathbf{h}^T_{1,i})(\phi_i \mathbf{h}_{2,i}\mathbf{h}^T_{1,i})^H$) and non-cross types (e.g $\mG (\phi_i \mathbf{h}_{2,i}\mathbf{h}^T_{1,i})^H$). For non-cross types, the phase terms will always cancel out ($\phi_i \phi_i^H = 1$). For the cross-terms, note that
	for each term in the polynomial, the hermetian of the term is also in the polynomial sum (e.g both $\mG (\phi_i \mathbf{h}_{2,i}\mathbf{h}^T_{1,i})^H$ and $ (\phi_i \mathbf{h}_{2,i}\mathbf{h}^T_{1,i}\mG^H$). Because $= trace(\mH^H) = trace(\mH)^*$, the complex component of these terms will always cancel. The result is that the phases, $\phi_i \forall i \in {1 \cdots	 K}$ will cancel out of the MSE expression. This result would hold for any linear-beamformer is used at the transmitter.
\bibliography{bibliography}
\end{document}

>>>>

	The IRS component of the channel can be decomposed in the paths through the individual elements as
	\mathbf{H}_{2}\boldsymbol{\Phi}\mathbf{H}_{1}= 
	\Sigma_{i=1}^{N_S} \phi_i \mathbf{h}_{2,i}\mathbf{h}^T_{1,i}
	for an IRS with $N_S$ reflective elements. 
In the following, we will assume that a matched filter is used at the transmitter. Further we will evaluate the performance of the system using the Mean Square Error given by 

@@

In the following we assume that the elements of the IRS can not only adjust the phases of the impinging waves but may also be "turned off" such that they are not included in the channel.
In order to minimize the overhead of pilot acquisition, we estimate the CSE in the following manner. 

@@

We leave all IRS elements \emph{on} to first find the full matched filter at the Tx. Assuming that we estimate the entire channel $\mH_{Total}$, we will not have sufficient information to estimate the individual components of the IRS component of the channel $\mathbf{h}_{2,i}\mathbf{h}^T_{1,i}$ and thus we cannot optimize with respect to $\phi_i $.

@@

	Next, by turning on a specific IRS element (can we use patterns using the correlation?) and sending additional pilots, we can estimate 

@@

E\left[\|  \vs - (\mG +  \mH_1 + \Sigma_{i=1}^{1} \phi_i \mathbf{h}_{2,i}\mathbf{h}^T_{1,i})(\mG +  \mH_1 + \Sigma_{i=1}^{1} \phi_i \mathbf{h}_{2,i}\mathbf{h}^T_{1,i})\vs  \|^2 \right]

@@

First, we rewrite the above utility function as
E\left[ trace\left((\vs - \mathbf{H}\mathbf{F}\vs)(\vs - \mathbf{H}\mathbf{F}\vs)^H \right)\right]
Assuming $\mathbf{H}$ and $\mathbf{F}$ to be constant over a coherence period, the expectation applies only to $\vs \vs^H$ to give
trace\left((\vs - \mathbf{H}\mathbf{F}\vs)(\vs - \mathbf{H}\mathbf{F}\vs)^H \right).

@@

	cross types (e.g $(\phi_i \mathbf{h}_{2,i}\mathbf{h}^T_{1,i})(\phi_i \mathbf{h}_{2,i}\mathbf{h}^T_{1,i})^H$) and non-cross terms (e.g $\mG (\phi_i \mathbf{h}_{2,i}\mathbf{h}^T_{1,i})^H$). For non-cross terms, the phases will always cancel out ($\phi_i \phi_i^H = 1$). For the cross-terms, note that
	for each term in the polynomial, the hermetian of the term is also in the polynomial sum (e.g both $\mG (\phi_i \mathbf{h}_{2,i}\mathbf{h}^T_{1,i})^H$ and $ (\phi_i \mathbf{h}_{2,i}\mathbf{h}^T_{1,i}\mG^H$). Because $= trace(\mH^H) = trace(\mH)^*$, the complex component of these terms will always cancel. The result is that the phases, $\phi_i  \;\forall i \in {1 \cdots	 K}$ will cancel out of the MSE expression. This result would hold for any linear-beamformer is used at the transmitter.
\section{Numerical Inconsistency}
Why is it that in the numerical results, the phase does have an impact on the MSE.

\bibliography{bibliography}
\end{document}
